Share Buyback and Equity Issue Anomalies Revisited

### 2016-02-15 bb_issuers.Rnw
updating tool

#load("tmpfiles/bb_issuersALL.Rdata")
reload_data = 1

# Then to make it into Word: 
# pandoc -s bb_issuers.tex --bibliography=bibliography.bib --number-sections --reference-links -o wordfilename.docx

@@

%Blind title page
\begin{titlepage}
\begin{center}
%  \centering
\vskip 60pt
\LARGE Share Buyback and Equity Issue Anomalies Revisited \par
\vskip 1.5em
\normalsize  \today
\noindent \\ 
\begin{abstract}
\noindent We re-examine the behavior of stock returns after share buyback and equity issuance announcements using the five-factor model proposed by \cite{FamaFrench2015a}. We confirm the findings of \cite{FamaFrench2015b} that the equity issue anomaly, i.e., the fact that equity issues are followed by negative long-term excess returns, disappears after replacing the \cite{FamaFrench1993} three-factor model with the five-factor model. However, long term positive excess returns after buyback announcements, first reported by Ikenberrry, Lakonishok and Vermaelen (1995), remain economically and statistically significant. Moreover, the Undervaluation Index proposed by \cite{PeyerVermaelen2009} remains a useful proxy for the likelihood that the buyback is driven by undervaluation. The buyback anomaly is robust over time and across sectors. Firms with low correlations with the market seem to be better at market timing, which is consistent with the hypothesis that the repurchase is driven by superior company-specific information. Firms with high pre-announce stock returns volatility also have higher abnormal returns, which is consistent with the hypothesis that a repurchase authorization is an option to take advantage of undervaluation as argued by Ikenberry and Vermaelen (1996). Finally, based on these findings, we develop an enhanced Undervaluation Index that improves abnormal returns relative to the index developed by \cite{PeyerVermaelen2009}.
\end{abstract}

\vspace{2cm}

\end{center}

\end{titlepage}

@@

\vspace{-.2in}
\begin{abstract}
\noindent We re-examine the behavior of stock returns after share buyback and equity issuance announcements using the five-factor model proposed by \cite{FamaFrench2015a}. We confirm the findings of \cite{FamaFrench2015b} that the equity issue anomaly, i.e., the fact that equity issues are followed by negative long-term excess returns, disappears after replacing the \cite{FamaFrench1993} three-factor model with the five-factor model. However, long term positive excess returns after buyback announcements, first reported by Ikenberrry, Lakonishok and Vermaelen (1995), remain economically and statistically significant. Moreover, the Undervaluation Index proposed by \cite{PeyerVermaelen2009} remains a useful proxy for the likelihood that the buyback is driven by undervaluation. The buyback anomaly is robust over time and across sectors. Firms with low correlations with the market seem to be better at market timing, which is consistent with the hypothesis that the repurchase is driven by superior company-specific information. Firms with high pre-announce stock returns volatility also have higher abnormal returns, which is consistent with the hypothesis that a repurchase authorization is an option to take advantage of undervaluation as argued by Ikenberry and Vermaelen (1996). Finally, based on these findings, we develop an enhanced Undervaluation Index that improves abnormal returns relative to the index developed by \cite{PeyerVermaelen2009}.

@@

Finally, the long-term event studies do not give much guidance about when to sell after a buyback or cover after shorting an equity issue. Trading strategies, such as $M\&A$ arbitrage (\cite{MitchellPulvino2001}), often have ``natural'' exit decision points (e.g., at $M\&A$ deal completion or termination), but the literature does not provide clear guidance about when to exit a buyback position.  Empirical studies tend to show that, on average, excess returns continue for up to 3 or 4 years after a buyback authorization, but there is no reason why such a horizon is optimal. The passive nature of the strategy may also give the impression that the strategy is too simple to justify management fees. One straightforward ``early'' selling strategy that we study is to combine the buyback and equity issuance anomalies by selling buyback stocks after the firm announces an equity issue. Note that the fact that equity issues in general are followed by negative abnormal returns does not necessarily imply that equity issues after buybacks should generate the same result. Given our focus on buybacks and equity issuance, we do not study other possible exit signals, such as missing analysts' estimates (e.g., \cite{PeyerVermaelen2009}), take over bids (e.g., \cite{Linetal2014}), or other company events.

The purpose of this paper is to explore these concerns by studying the robustness of the buybacks and issuance anomalies over the 30 year period starting in January \Sexpr{firstyear} and ending in December \Sexpr{lastyear}, using the \cite{FamaFrench2015a} five-factor model. Although there are other models of market equilibrium proposed to explain excess returns after buyback authorizations (i.e. \cite{Linetal2014}) our focus is on the \cite{FamaFrench2015a} challenge. We are also agnostic on the source of misvaluation, e.g., undervaluing cash flows or overestimating risk (\cite{GrullonMichaely2004}). We confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant. Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio. The interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive.

We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns and that the anomaly does not disappear if we exclude specific industries.  Moreover, the predictive capacity can be significantly enhanced if we incorporate two additional indicators that are expected to be correlated with misvaluation. First,  idiosyncratic risk, which measures to what extent stock prices are driven by company-specific information. Unlike \cite{Ang2006}, who find a negative relation between idiosyncratic volatility and future returns, and \cite{FamaFrench2015b}, who show similar evidence for small firms, we find  
a positive relation for buyback stocks. This is consistent with \cite{Stambaugh2015} who find a positive relation for undervalued\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  stocks. The second indicator to be correlated with misvaluation is  volatility. The argument is that a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks (\cite{IkenberryVermaelen1996}). Combining these new measures with the Peyer-Vermaelen (2009) Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns. In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method. Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.

@@

To further study the robustness of the buyback anomaly over time, we simulate a portfolio investment strategy starting in \Sexpr{firstyear}. The strategy uses past data to estimate the factor betas and measures the abnormal returns of buyback portfolios over different investment horizons. While this is not an accurate measure of the returns of a buyback fund - as we do not consider transaction costs, turnover issues, or other operational issues (see for example \cite{MitchellPulvino2001}) - it provides us with an estimate of what would have happened to an investor who starts investing in \Sexpr{firstyear} in an equally weighted portfolio of buyback stocks and holds them over various horizons.

@@

Note that, as there is no hindsight and all betas are estimated every month using past data, the portfolio used to estimate the betas may consist of firms that are different from those of the (newly created) portfolio that is hedged - as we do not know when companies will announce a buyback. On the other hand, note that unlike this strategy, both the IRATs and calendar event study results use hindsight to estimate risk. However, despite using pre-portfolio formation data to estimate the betas, the returns of the overall strategy have very low betas with the five factors.\footnote{For example for the $N =12$ months holding period discussed below, the betas for the five factors Market, SMB, HML, RMW, and CMA are respectively \Sexpr{round(expost_betas[2,1],3)}, \Sexpr{round(expost_betas[3,1],3)}, \Sexpr{round(expost_betas[4,1],3)}, \Sexpr{round(expost_betas[5,1],3)} and \Sexpr{round(expost_betas[6,1],3)}. The corresponding betas for the ``unhedged'' strategy are \Sexpr{round(expost_betas_unhedged[2,1],3)}, \Sexpr{round(expost_betas_unhedged[3,1],3)}, \Sexpr{round(expost_betas_unhedged[4,1],3)}, \Sexpr{round(expost_betas_unhedged[5,1],3)} and \Sexpr{round(expost_betas_unhedged[6,1],3)}. This also indicates that the returns shown in Figure~\ref{fig:ReturnsBB} and Table~\ref{tbl:allhedgedBB} are close to excess returns. Getting pure excess returns in practice requires more detailed hedging (without hindsight). }

@@

@@

\section{Enhancing the U-index: \\
Idiosyncratic Risk and Volatility}
\label{sec:infoassymetry}

@@

The main ``theory'' behind the buyback anomaly is that firms may have superior {\it company-specific} information. Such situations are more likely in industries or companies where the value is driven less by market wide factors, i.e., by highly ``idiosyncratic'' companies.  To test this hypothesis, for each event we measure the five-factor regression $R^2$ using the 6-months daily returns just before the event announcement.\footnote{Using shorter time windows, e.g., 1 month, or using the idiosyncratic volatility as in \cite{Ang2006}, leads to the same conclusions - results available upon request. However, as we want to differentiate between ``idiosyncratic'' companies and ``high volatility'' ones, to consider both the effects of company specific information and of the option value of a buyback announcement, we separately study the relations with $R^2$ and volatility. See also \cite{Lietal2014} for a discussion on this issue.} We define two types of events: ``low idiosyncratic'' (high $R^2$) and ``high idiosyncratic'' (low $R^2$) events, depending on whether the five-factor regression $R^2$ was in the top or bottom \Sexpr{round(100*quantile_R2,2)}$\%$ of the $R^2$ of all CRSP companies: each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' five-factor regression $R^2$. We also define the idiosyncratic score of a firm to be the percentile of its $1-R^2$ across all CRSP firms that month. Note that we do not need to  define 20 breakpoints as Fama-French do, and for simplicity we focus on the two extreme quantiles only. Table~\ref{tbl:industriesR2Vol}, columns (1) and (2) show the percentage of high and low idiosyncratic risk events across all industries for which we have at least 100 buyback events in our sample. The healthcare industry has the largest percentage of firms classified as ``high idiosyncratic'', while cyclical industries such as steel, construction and chemicals contain a large number of ``low idiosyncratic'' firms.

Figure~\ref{fig:badpreviousR2}  shows the results of a strategy similar to the strategy of Figure~\ref{fig:ReturnsBB} (Panel~B): starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous N months and hold the stock for $N$ months. The graph shows two strategies, one for a short holding period ($N=12$) and one for a very long holding period ($N=48$). In both cases the excess returns for high idiosyncratic companies are higher.  Specifically, high idiosyncratic companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_Idiosyncr_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_Idiosyncr_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy. These excess returns are higher than the \Sexpr{round(tail(cumsum(100*Low_Idiosyncr_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_Idiosyncr_BB_Hedged48m),1),1)}$\%$) of the corresponding low idiosyncratic sample.

Table~\ref{tbl:IdiosyncraticunderBB}  confirms this result in a more systematic way. It shows the IRATS and Calendar Time abnormal returns for high and low idiosyncratic buyback events-companies. Focusing on IRATS, high idiosyncratic buyback stocks earn \Sexpr{R2_IRATStableBB["+48","High Idiosync.: CAR"]}$\%$  after 48 months, more than three times the excess returns of the low idiosyncratic announcements. The results using the Calendar Time method confirm these findings.

Table~\ref{tbl:IdiosyncraticunderBB} also tests whether adjusting for idiosyncratic risk improves the predictive power of the U-index. Regardless of the time horizon and the event study method, the U-index works only for idiosyncratic companies. After 48 months, based on the IRATS methods, high U-index high idiosyncratic companies earn \Sexpr{R2_IRATStable_underBB["+48","High Idiosync.: U CAR"]}$\%$ (t=\Sexpr{R2_IRATStable_underBB["+48",8]}). Low idiosyncratic high U-index firms have only an insignificant excess return of \Sexpr{R2_IRATStable_underBB["+48",1]}$\%$ (t=\Sexpr{R2_IRATStable_underBB["+48",2]}), while for low idiosyncratic firms the low U-index IRATS excess returns are significant (\Sexpr{R2_IRATStable_underBB["+48",4]}$\%$, t=\Sexpr{R2_IRATStable_underBB["+48",5]}).  Note however that we only have few events in low idiosyncratic, high U-index (\Sexpr{R2_IRATStable_underBB["Observations",1]} events) and high idiosyncratic, low U-index (\Sexpr{R2_IRATStable_underBB["Observations",10]} events) categories. The Calendar Time results provide the same picture: only for the high idiosyncratic, high U-index firms we obtain significant (t=\Sexpr{R2_IRATStable_underBB_cal["+48",8]}) monthly excess returns of \Sexpr{R2_IRATStable_underBB_cal["+48",7]}$\%$. The high idiosyncratic and low U-index firms have  non-significant (t=\Sexpr{R2_IRATStable_underBB_cal["+48",11]}) monthly excess returns of \Sexpr{R2_IRATStable_underBB_cal["+48",10]}$\%$.

@@

The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \cite{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns. This is commonly referred to as the volatility puzzle. However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks. Their argument is that IVOL represents risk that deters arbitrage and therefore creates mispricing. Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between IVOL and future returns for undervalued stocks.  Their most under-priced high IVOL stocks earn monthly excess returns (relative to the Fama-French three-factor model) of 0.56$\%$ per month which is quite similar to the \Sexpr{R2_IRATStableBB_cal["+48","High Idiosync.: CAL"]}$\%$ per month reported in our Table~\ref{tbl:IdiosyncraticunderBB} Panel B (using the five-factor model).

@@

The announcement of a buyback program is not a firm commitment, but an option to buy back stock. Ikenberry and Vermaelen (1996) model this flexibility as an exchange option in which the market price of the stock is exchanged for the true value of the stock. They predict that, as with all options, the value increases with the volatility. The intuition is that the larger the volatility, the larger the probability that the market price may deviate from the true value. This enhances the timing ability of the manager-insider. Hence, perhaps total volatility is a better prediction of excess returns than idiosyncratic volatility or the U-index.  Or perhaps volatility can be an additional, next to the U-index and idiosyncratic volatility, indicator of the likelihood that the buyback is driven by undervaluation.

@@

Figure~\ref{fig:badpreviousVOL} shows the results of a strategy similar to the strategy of Figure~\ref{fig:ReturnsBB}: starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months. The graph shows two strategies, one for a short holding period ($N=12$) and one for a very long holding period ($N=48$). In both cases the excess returns for high volatility companies is higher. Specifically, high volatility companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy, which are higher than the \Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged48m),1),1)}$\%$) of the corresponding low volatility sample.

Table~\ref{tbl:VOLunderBB} confirms this result in a more systematic way. It shows the IRATS and Calendar Time abnormal returns for high and low volatility buybacks events-companies. Focusing on IRATS, high volatility buyback stocks earn \Sexpr{VOL_IRATStableBB["+48","High Vol: CAR"]}$\%$  after 48 months, while low volatility events have non significant abnormal returns for any period. The results using the Calendar Time method confirm these findings.

>>>>

#load("tmpfiles/bb_issuersALL.Rdata")
reload_data = 0

# Then to make it into Word: 
# pandoc -s bb_issuers.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx

@@

%%Blind title page
%\begin{titlepage}
%\begin{center}
%  \centering
%\vskip 60pt
%\LARGE Share Buyback and Equity Issue Anomalies Revisited \par
%\vskip 1.5em
%\normalsize  \today
%\noindent \\ 
%\begin{abstract}
%\noindent We re-examine the behavior of stock returns after share buyback and equity issuance announcements using the five-factor model proposed by \cite{FamaFrench2015a}. We confirm the findings of \cite{FamaFrench2015b} that the equity issue anomaly, i.e., the fact that equity issues are followed by negative long-term excess returns, disappears after replacing the \cite{FamaFrench1993} three-factor model with the five-factor model. However, long term positive excess returns after buyback announcements, first reported by \cite{IkenberryLakonishokVermaelen1995}, remain economically and statistically significant. Moreover, the Undervaluation Index proposed by \cite{PeyerVermaelen2009} remains a useful proxy for the likelihood that the buyback is driven by undervaluation. The buyback anomaly is robust over time and across sectors. Firms with low correlations with the market seem to be better at market timing, which is consistent with the hypothesis that the repurchase is driven by superior company-specific information. Firms with high pre-announce stock returns volatility also have higher abnormal returns, which is consistent with the hypothesis that a repurchase authorization is an option to take advantage of undervaluation as argued by \cite{IkenberryVermaelen1996}. This result is also consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks, unlike the well-known low volatility anomaly across all stocks. Finally, based on these findings, we develop an enhanced Undervaluation Index that improves abnormal returns relative to the index developed by \cite{PeyerVermaelen2009}.
%\end{abstract}
%\vspace{2cm}
%\end{center}
%\medskip
%\noindent \textit{JEL classification}: G35
%\medskip
%\noindent \textit{Keywords}: Share Buybacks, Seasoned Equity Offerings
%\end{titlepage}

@@

\vspace{-.2in}
\begin{abstract}
\noindent We re-examine the behavior of stock returns after share buyback and equity issuance announcements using the five-factor model proposed by \cite{FamaFrench2015a}. We confirm the findings of \cite{FamaFrench2015b} that the equity issue anomaly, i.e., the fact that equity issues are followed by negative long-term excess returns, disappears after replacing the \cite{FamaFrench1993} three-factor model with the five-factor model. However, long term positive excess returns after buyback announcements, first reported by \cite{IkenberryLakonishokVermaelen1995}, remain economically and statistically significant. Moreover, the Undervaluation Index proposed by \cite{PeyerVermaelen2009} remains a useful proxy for the likelihood that the buyback is driven by undervaluation. The buyback anomaly is robust over time and across sectors. Firms with low correlations with the market seem to be better at market timing, which is consistent with the hypothesis that the repurchase is driven by superior company-specific information. Firms with high pre-announce stock returns volatility also have higher abnormal returns, which is consistent with the hypothesis that a repurchase authorization is an option to take advantage of undervaluation as argued by \cite{IkenberryVermaelen1996}. This result is also consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks, unlike the well-known low volatility anomaly across all stocks. Finally, based on these findings, we develop an enhanced Undervaluation Index that improves abnormal returns relative to the index developed by \cite{PeyerVermaelen2009}.

@@

The long-term event studies also do not give much guidance about when to sell after a buyback or cover after shorting an equity issue. Trading strategies, such as $M\&A$ arbitrage (\cite{MitchellPulvino2001}), often have ``natural'' exit decision points (e.g., at $M\&A$ deal completion or termination), but the literature does not provide clear guidance about when to exit a buyback position.  Empirical studies tend to show that, on average, excess returns continue for up to 3 or 4 years after a buyback authorization, but there is no reason why such a horizon is optimal. One straightforward ``early'' selling strategy that we study is to combine the buyback and equity issuance anomalies by selling buyback stocks after the firm announces an equity issue. Note that the fact that equity issues in general are followed by negative abnormal returns does not necessarily imply that equity issues after buybacks should generate the same result.

Finally, the results from event studies which use either Ibbotson RATS or the Calendar Time method estimate excess returns and risks contemporaneously. Investors, such as hedge funds, who would like to exploit the anomaly and hedge market risk need however to estimate the factor betas using historical information. If the buyback signals a change in risk (\cite{GrullonMichaely2004}) hedging market risk may be complicated. That is why in this paper we also simulate hedged investment strategies where we estimate risk {\it before} forming the portfolios.

The purpose of this paper is to explore these concerns by studying the robustness of the buybacks and issuance anomalies over the 30 year period starting in January \Sexpr{firstyear} and ending in December \Sexpr{lastyear}, using the \cite{FamaFrench2015a} five-factor model. Although there are other models of market equilibrium proposed to explain excess returns after buyback authorizations (i.e. \cite{Linetal2014}) our focus is on the \cite{FamaFrench2015a} challenge.  We confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant. Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio. The interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive. We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms, and that the anomaly does not disappear if we exclude specific industries.

We also test whether the buyback anomaly is related to the even better known {\it low volatility anomaly}: that (idiosyncratic) volatility is negatively related to future returns. For example, \cite{Ang2006} find negative alphas for high volatility and high idiosyncratic volatility stocks, using the 3 factor \cite{FamaFrench1993} model. Moreover, \cite{FamaFrench2015b} show that, using the 5-factor model, this anomaly persists for small firms. However, in our buyback sample we find a significant positive relation between excess returns, using  the Fama-French 5-factor model as a benchmark. This is consistent with the {\it information advantage hypothesis}: in firms with high idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market. The result is also consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  stocks.

Turning to total volatility we also find that buyback authorizations of high risk stocks are followed by larger excess returns. This is consistent with the {\it option hypothesis}:  a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks (\cite{IkenberryVermaelen1996}). If markets underestimate the value of this option at the time of the buyback authorization, excess returns should be positively correlated with volatility.  Combining idiosyncratic risk and total volatility  with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns. In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method. Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.

@@

\subsection{Robustness with respect to estimation of factor betas}
\label{sec:robustbeta}

Note that both event study methods measure alpha (excess return) and betas jointly. In other words, we do not use prior (to investing) information to estimate risk. An investor who wants to exploit the anomaly, however, may want to hedge market (and other) risk and would need to estimate betas using past data. If the buyback signals a change in risk (\cite{GrullonMichaely2004}) it is not obvious that such a hedged strategy would work.

To further study the robustness of the buyback anomaly, we simulate a portfolio investment strategy starting in \Sexpr{firstyear}. The strategy uses past data to estimate the factor betas and measures the abnormal returns of buyback portfolios over different investment horizons. While this is not an accurate measure of the returns of a buyback fund - as we do not consider transaction costs, turnover issues, or other operational issues (see for example \cite{MitchellPulvino2001}) - it provides us with an estimate of what would have happened to an investor who starts investing in \Sexpr{firstyear} in an equally weighted portfolio of buyback stocks and holds them over various horizons.

@@

@@

Despite using pre-portfolio formation data to estimate the betas, unlike both the IRATs and Calendar Time methods that use hindsight to estimate risk, the hedged portfolio has very low betas with the five factors. For example for the $N =12$ months holding period, the betas for the five factors Market, SMB, HML, RMW, and CMA are respectively \Sexpr{round(expost_betas[2,1],3)}, \Sexpr{round(expost_betas[3,1],3)}, \Sexpr{round(expost_betas[4,1],3)}, \Sexpr{round(expost_betas[5,1],3)} and \Sexpr{round(expost_betas[6,1],3)}. The corresponding betas for the ``unhedged'' strategy are \Sexpr{round(expost_betas_unhedged[2,1],3)}, \Sexpr{round(expost_betas_unhedged[3,1],3)}, \Sexpr{round(expost_betas_unhedged[4,1],3)}, \Sexpr{round(expost_betas_unhedged[5,1],3)} and \Sexpr{round(expost_betas_unhedged[6,1],3)}. This also indicates that the returns shown in Figure~\ref{fig:ReturnsBB} and Table~\ref{tbl:allhedgedBB} are close to ``excess'' returns, i.e. returns that have basically eliminated all factors risk. This is also consistent with the hypothesis that the buyback announcement itself does not materially change the risk of the repurchasing firms (in the short term).

@@

\section{Excess returns and volatility}
\label{sec:infoassymetry}

There exists a large literature on volatility and stock returns. One of the most puzzling findings is the fact that total volatility and idiosyncratic volatility are negatively correlated with future abnormal returns, when expected returns are calculated using the 3 factor \cite{FamaFrench1993} model  (see e.g. \cite{Ang2006} (Table VII)). This volatility anomaly also survives after using the \cite{FamaFrench2015a} 5-factor model, at least for small firms.  Perhaps the buyback and the volatility anomaly are related: are the buyback firms with the largest excess returns also firms with the smallest (idiosyncratic) risk?  Or can we make arguments that the opposite is true, if we accept the fundamental proposition of this paper, i.e. that excess returns are a result of the fact that managers are on average successful in taking advantage of an undervalued stock price?

@@

The main ``theory'' behind the buyback anomaly is that firms may have superior {\it company-specific} information. Such situations are more likely in industries or companies where the value is driven less by market wide factors, i.e., by highly ``idiosyncratic'' companies.  So if buybacks are driven by market timing this superior information hypothesis predicts that there should be a positive relation between idiosyncratic returns and volatility.  To test this hypothesis, for each event we measure the five-factor regression $R^2$ using the 6-months daily returns just before the event announcement.\footnote{Using shorter time windows, e.g., 1 month, or using the idiosyncratic volatility as in \cite{Ang2006}, leads to the same conclusions - results available upon request. However, as we want to differentiate between ``idiosyncratic'' companies and ``high volatility'' ones, to consider both the effects of company specific information and of the option value of a buyback announcement, we separately study the relations with $R^2$ and volatility. See also \cite{Lietal2014} for a discussion on this issue.} We define two types of events: ``low idiosyncratic'' (high $R^2$) and ``high idiosyncratic'' (low $R^2$) events, depending on whether the five-factor regression $R^2$ was in the top or bottom \Sexpr{round(100*quantile_R2,2)}$\%$ of the $R^2$ of all CRSP companies: each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' five-factor regression $R^2$. We also define the idiosyncratic score of a firm to be the percentile of its $1-R^2$ across all CRSP firms that month. Note that we do not need to  define 20 breakpoints as Fama-French do, and for simplicity we focus on the two extreme quantiles only. Table~\ref{tbl:industriesR2Vol}, columns (1) and (2) show the percentage of high and low idiosyncratic risk events across all industries for which we have at least 100 buyback events in our sample. The healthcare industry has the largest percentage of firms classified as ``high idiosyncratic'', while cyclical industries such as steel, construction and chemicals contain a large number of ``low idiosyncratic'' firms.

Table~\ref{tbl:IdiosyncraticunderBB} shows the IRATS and Calendar Time abnormal returns for high and low idiosyncratic buyback events-companies. Focusing on IRATS, high idiosyncratic buyback stocks earn \Sexpr{R2_IRATStableBB["+48","High Idiosync.: CAR"]}$\%$  after 48 months, more than three times the excess returns of the low idiosyncratic announcements. The results using the Calendar Time method confirm these findings. Table~\ref{tbl:IdiosyncraticunderBB} also tests whether adjusting for idiosyncratic risk improves the predictive power of the U-index. Regardless of the time horizon and the event study method, the U-index works only for idiosyncratic companies. After 48 months, based on the IRATS methods, high U-index high idiosyncratic companies earn \Sexpr{R2_IRATStable_underBB["+48","High Idiosync.: U CAR"]}$\%$ (t=\Sexpr{R2_IRATStable_underBB["+48",8]}). Low idiosyncratic high U-index firms have only an insignificant excess return of \Sexpr{R2_IRATStable_underBB["+48",1]}$\%$ (t=\Sexpr{R2_IRATStable_underBB["+48",2]}), while for low idiosyncratic firms the low U-index IRATS excess returns are significant (\Sexpr{R2_IRATStable_underBB["+48",4]}$\%$, t=\Sexpr{R2_IRATStable_underBB["+48",5]}).  Note however that we only have few events in low idiosyncratic, high U-index (\Sexpr{R2_IRATStable_underBB["Observations",1]} events) and high idiosyncratic, low U-index (\Sexpr{R2_IRATStable_underBB["Observations",10]} events) categories. The Calendar Time results provide the same picture: only for the high idiosyncratic, high U-index firms we obtain significant (t=\Sexpr{R2_IRATStable_underBB_cal["+48",8]}) monthly excess returns of \Sexpr{R2_IRATStable_underBB_cal["+48",7]}$\%$. The high idiosyncratic and low U-index firms have  non-significant (t=\Sexpr{R2_IRATStable_underBB_cal["+48",11]}) monthly excess returns of \Sexpr{R2_IRATStable_underBB_cal["+48",10]}$\%$.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B). Starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months. High idiosyncratic companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_Idiosyncr_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_Idiosyncr_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy. These excess returns are higher than the \Sexpr{round(tail(cumsum(100*Low_Idiosyncr_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_Idiosyncr_BB_Hedged48m),1),1)}$\%$) of the corresponding low idiosyncratic sample.}

@@

The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \cite{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns. However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks. Their argument is that IVOL represents risk that deters arbitrage and therefore creates mispricing. Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between IVOL and future returns for undervalued stocks.  Their most under-priced high IVOL stocks earn monthly excess returns (relative to the Fama-French three-factor model) of 0.56$\%$ per month which is quite similar to the \Sexpr{R2_IRATStableBB_cal["+48","High Idiosync.: CAL"]}$\%$ per month reported in our Table~\ref{tbl:IdiosyncraticunderBB} Panel B (using the five-factor model).

@@

The announcement of a buyback program is not a firm commitment, but an option to buy back stock. Ikenberry and Vermaelen (1996) model this flexibility as an exchange option in which the market price of the stock is exchanged for the true value of the stock. They predict that, as with all options, the value increases with the volatility. The intuition is that the larger the volatility, the larger the probability that the market price may deviate from the true value. This enhances the timing ability of the manager-insider.  They show that this option can have a lot of value, something that may not be realized at the time of the announcement of the buyback authorization.  Hence, perhaps total volatility is a better prediction of excess returns than idiosyncratic volatility or the U-index.  Or perhaps volatility can be an additional, next to the U-index and idiosyncratic volatility, indicator of the likelihood that the buyback is driven by undervaluation.

@@

Table~\ref{tbl:VOLunderBB} shows the IRATS and Calendar Time abnormal returns for high and low volatility buybacks events-companies. Focusing on IRATS, high volatility buyback stocks earn \Sexpr{VOL_IRATStableBB["+48","High Vol: CAR"]}$\%$  after 48 months, while low volatility events have non significant abnormal returns for any period. The results using the Calendar Time method confirm these findings.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B). Starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months. High volatility companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy, which are higher than the \Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged48m),1),1)}$\%$) of the corresponding low volatility sample.}

Table~\ref{tbl:VOLunderBB} also tests whether the U-index is valid for high volatility events, as well as whether adjusting for volatility improves the predictive power of the U-index. Regardless of the time horizon and the event study method, the U-index works for high volatile companies. After 48 months, based on the IRATS methods, high U-index high volatility companies earn \Sexpr{VOL_IRATStable_underBB["+48","High Vol: U CAR"]}$\%$ (t = \Sexpr{VOL_IRATStable_underBB["+48",8]}). Low U-index high volatility companies earn \Sexpr{VOL_IRATStable_underBB["+48",10]}$\%$ (t = \Sexpr{VOL_IRATStable_underBB["+48",11]}). The Calendar Time results provide the same picture. Figure~\ref{fig:pastallVOL} summarizes the results for the total sample and the high and low U-index sample. The main difference with Figure~\ref{fig:pastallidio} is that now also low volatility/high U-index firms earn significant excess returns of \Sexpr{VOL_IRATStable_underBB["+48",1]}$\%$ after 48 months.
